---
title: "Embedding Gadfly plots in HTML with knitr & R Markdown"
author: "Carson Sievert"
date: "August 28, 2014"
output:
  ioslides_presentation:
    incremental: yes
    widescreen: yes
---

```{r set-hook, echo=FALSE}
library(knitr)
opts_chunk$set(tidy = F, comment = "#>")
# thanks Ramnath -- https://ramnathv.github.io/posts/verbatim-chunks-knitr/
knit_hooks$set(source = function(x, options){
  if (!is.null(options$verbatim) && options$verbatim){
    opts = gsub(",\\s*verbatim\\s*=\\s*TRUE\\s*", "", options$params.src)
    bef = sprintf('\n\n    ```{r %s}\n', opts, "\n")
    stringr::str_c(
      bef, 
      knitr:::indent_block(paste(x, collapse = '\n'), "    "), 
      "\n    ```\n"
    )
  } else {
    stringr::str_c("\n\n```", tolower(options$engine), "\n", 
      paste(x, collapse = '\n'), "\n```\n\n"
    )
  }
})
```


## knitr engines
* knitr has built-in support for some "engines" including (but not limited to):
    * "popular" languages (python, perl, fortran, haskell, etc.)
    * various "command-line tools" (sed, awk, bash, sh, zsh, etc.)
* Unfortunately, for each knitr chunk that does __not__ have `'R'` as it's `engine` option
    * a new session is opened
    * code is parsed and evaluated in that session (or set `eval = FALSE`)
    * results are returned and the session is closed
* Opening & closing sessions can be expensive, so ideally, we open __one__ new session and only ship code when necessary. 
    * Yihui wrote the [runr](https://github.com/yihui/runr) package with this idea in mind.
  
## A julia engine for knitr!

```{r setup, verbatim = TRUE}
library(knitr)
library(runr)
j = proc_julia()
j$start()
knit_engines$set(julia = function(options) {
    knitr:::wrap(j$exec(options$code), options)
})
```

```{r hello, verbatim = TRUE, engine = 'julia'}
string("Hello", " World!")
```

## Now using Gadfly!

```{r gadfly, eval = FALSE}
using Gadfly
myplot = plot(x = rand(30), y = rand(30));
draw(SVGJS(string("myplot.svg"), 3inch, 2inch), myplot);
```

<div align = "center">
  <object data="myplot.svg" type="image/svg+xml" width="600" height="400"></object>
</div>


## More Gadfly

## Drawbacks to `engine = 'julia'`

* `cache = TRUE` doesn't really work
    * Loading workspace(s) is fairly trivial for R, but how does this work for julia (or other languages for that matter?)
* Do IPython/IJulia suffer from these same drawbacks?


## Make sure to stop the julia session!

```{r stop-julia}
j$stop()
```